Synthesizing Quotient Lenses

### 2018-03-15 papers/QuotientLenses/main.tex
tweaks to the intro

For example, consider the following QRE for writing author
names:\bcp{Solomon: Someone noted on their copy of the intro from
  class yesterday that this example is backwards.  Did you go over the
  marked-up copies that I gave you?}\sam{I'm not sure what this comment means
  and also I forgot those notes in the office. I'll go through them more
  thoroughly tomorrow morning.}\bcp{What the comment means is that names are
not usually formatted as ``Solomon, Maina'' but rather as ``Maina, Solomon''.}
%
\begin{lstlisting}
let wsp_sp = collapse wsp $\to$ " "
let comma_name = first_name . "," . wsp_sp . last_name
\end{lstlisting}
%
In this example, \lstinline{wsp} is an existing regular expression for a
nonempty sequence of whitespace characters, and \lstinline{first_name} and
\lstinline{last_name} are existing regular expressions for first and last names.
The QRE \lstinline{wsp_sp} is a QRE with the same underlying language as
\lstinline{wsp}, but with a single canonical representative: \lstinline{" "}.
This is then used to build up \lstinline{comma_name}, a QRE with an
underlying language of two names, separated by a command and whitespace, where
the names with a single space between them are canonical.

>>>>

For example, consider the following QRE for writing author
names:
%
\begin{lstlisting}
let wsp_sp = collapse wsp $\to$ " "
let comma_name = last_name . "," . wsp_sp . first_name
\end{lstlisting}
%
In this example, \lstinline{wsp} is an existing regular expression for a
nonempty sequence of whitespace characters, and \lstinline{first_name} and
\lstinline{last_name} are existing regular expressions for first and last names.
The QRE \lstinline{wsp_sp} is a QRE with the same underlying language as
\lstinline{wsp}, but with a single canonical representative: \lstinline{" "}.
It is used as a component of \lstinline{comma_name}, a QRE with an
underlying language of two names, separated by a command and whitespace, where
the names with a single space between them are canonical.
